### 2016-09-29 rebuttal.tex

  \begin{enumerate}
  \item We have renamed the ``Features'' section to ``Overview of
    Capabilities'', now section~\ref{P-sec:features}.
  \item We have renamed the ``Domain Specific Submodules'' section to
      ``Physics Submodule'', now section~\ref{P-sec:domain_specific} (see point~\ref{rev3point30}).
  \item We have moved the ``Architecture'' section to the end, after the
    ``Physics Submodule'' section. It is now section~\ref{P-sec:architecture}.
  \item We have moved the ``Basic Usage'' subsection to the beginning of the
    ``Overview of Capabilities'' section (it is now section~\ref{P-sec:basic-usage}), and added an intro paragraph to the
    ``Overview of Capabilities'' section.
  \item We have moved the ``Assumptions'' subsection to the ``Overview of
    Capabilities'' subsection, after the features table. It is now section~\ref{P-sec:assumptions}.
  \item The ``Comparison with Mathematica'' section has been moved to the end of
    the supplement, now section~\ref{S-suppsec:comp-mma}.
  \item The ``Other Projects that
      Depend on SymPy'' section (which has been renamed from ``Other Projects that
      Use SymPy'') has been moved from the supplement to the main paper
      content, now section~\ref{P-sec:other-proj}.
  \end{enumerate}

We disagree with the reviewer on a few points. We do not consider SymPy Live
or SymPy Gamma to be key components of SymPy. The goal of the paper is
to be about the SymPy library. While SymPy Live and SymPy Gamma are
maintained by the SymPy community, they are separate projects. A
mention of SymPy Live has been added to the introduction (see editor
point~\ref{editorpoint1}), as it may assist an interested reader in trying the
examples from the paper. A mention of SymPy Gamma has been added to the ``Projects that
Depends on SymPy'' table (Table~\ref{P-projects-table}), now part of the main
paper (see above). We have
left the more in-depth discussion of SymPy Gamma in the supplement (section~\ref{S-suppsec:sympy-gamma}).

### 2016-09-29 rebuttal.tex

The ``Comparison with Mathematica'' section has been placed in the supplement
because we do not feel that a treatment in the main manuscript would be fair
without an equal comparison to other principle computer algebra systems, such
as Maple, SageMath, and Maxima. Unfortunately, our authorship is inexpert in
these systems, so a complete and fair comparison is impossible.

We deem all the sections in section 3 (now section~\ref{P-sec:features}) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively:
\begin{itemize}
\item In SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}.

\item The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. It is out of
scope for an architecture paper.

\item The SymPy Live section was short and would be mostly duplicated by the
  mention that has been added to the introduction in the paper. We have thus
  removed it.
\end{itemize}

### 2016-09-29 rebuttal.tex

  \begin{enumerate}
  \item We have renamed the ``Features'' section to ``Overview of
    Capabilities'', now section~\ref{P-sec:features}.
  \item We have renamed the ``Domain Specific Submodules'' section to
      ``Physics Submodule'', now section~\ref{P-sec:domain_specific} (see point~\ref{rev3point30}).
  \item We have moved the ``Architecture'' section to the end, after the
    ``Physics Submodule'' section. It is now section~\ref{P-sec:architecture}.
  \item We have moved the ``Basic Usage'' subsection to the beginning of the
    ``Overview of Capabilities'' section (it is now section~\ref{P-sec:basic-usage}), and added an intro paragraph to the
    ``Overview of Capabilities'' section.
  \item We have moved the ``Assumptions'' subsection to the ``Overview of
    Capabilities'' subsection, after the features table. It is now section~\ref{P-sec:assumptions}.
  \item The ``Comparison with Mathematica'' section has been moved to the end of
    the supplement, now section~\ref{S-suppsec:comp-mma}.
  \item The ``Other Projects that
      Depend on SymPy'' section (which has been renamed from ``Other Projects that
      Use SymPy'') has been moved from the supplement to the main paper
      content, now section~\ref{P-sec:other-proj}.
  \end{enumerate}

We disagree with the reviewer on a few points. We do not consider SymPy Live
or SymPy Gamma to be key components of SymPy. The goal of the paper is
to be about the SymPy library. While SymPy Live and SymPy Gamma are
maintained by the SymPy community, they are separate projects. A
mention of SymPy Live has been added to the introduction (see editor
point~\ref{editorpoint1}), as it may assist an interested reader in trying the
examples from the paper. A mention of SymPy Gamma has been added to the ``Projects that
Depends on SymPy'' table (Table~\ref{P-projects-table}), now part of the main
paper (see above). We have
left the more in depth discussion of SymPy Gamma in the supplement (section~\ref{S-suppsec:sympy-gamma}).

@@

The ``Comparison with Mathematica'' section has been placed in the supplement
because we do not feel that a treatment in the main manuscript would be fair
without an equal comparison to other principle computer algebra systems, such
as Maple, SageMath, and Maxima. Unfortunately, our authorship is inexpert in
these systems, so a complete and fair comparison is impossible.

We deem all the sections in section 3 (now section~\ref{P-sec:features}) to be important core
components of the library. Regarding the supplement sections (previously) 5,
7, and 9---``Sets'', ``Category Theory'', and ``SymPy Live'',
respectively:
\begin{itemize}
\item In SymPy 1.0, the sets module is still in
a relatively infant stage. It is mentioned already in conjunction with the
\texttt{solveset} function. We have added some additional text to the solvers
subsection regarding \texttt{sympy.sets}.

\item The category theory module in SymPy
is very domain specific, and independent of other SymPy modules. It is out of
scope for an architecture paper.

\item The SymPy Live section was short and would be mostly duplicated by the
  paragraph that has been added to the introduction in the paper. We have thus
  removed it.
\end{itemize}

@@

\question It is unclear what ``both of these objects'' refer to in line 532. My guess is vectors and dyadic objects, but this should be reworded to make it more clear.
\begin{solution}
We have changed ``both of these objects can be written\ldots'' to ``the vector
and dyadic objects can both be written\ldots''.
\end{solution}

\question In lines 543 and 545, ``rad'' should be removed. Radians are assumed when no other measure (like degrees) is given.
\begin{solution}
These units were removed.
\end{solution}

\question In lines 567--568, ``performing symbolic quantum mechanics'' makes no sense. This should probably be ``computations'', ``solving problems related to'', etc.
\begin{solution}
This was reworded to:
\begin{quote}
to solve problems in quantum mechanics
\end{quote}
\end{solution}

\question The sentence ``SymPy expressions are immutable trees of Python objects.'' doesn't belong in the conclusion. This can be moved to the appropriate place when discussing SymPy's architecture.
\begin{solution}
This paper focuses on the architecture of SymPy, and we consider this to be a
core feature of SymPy's architecture, hence, it's inclusion in the conclusion.
We have also discussed the different points in this sentence in depth in the architecture section.
\end{solution}

### 2016-09-29 features.tex
Add a section label for the basic usage section
Change "in-depth" to "in depth" everywhere
Except for one place where it was in the reviewer's text.

% Features to discuss in-depth:
This section gives a basic introduction of SymPy, and lists its features.
A few features---assumptions, simplification, calculus, polynomials, printers,
solvers, and matrices---are core components of SymPy and are discussed in
depth. Many other features are discussed in depth in the supplementary
material.

\subsection{Basic Usage}
\input{basic_usage.tex}

@@

Although SymPy's extensive feature set cannot be covered in-depth in this
paper, calculus and other bedrock areas are discussed in their own
subsections. Additionally, Table~\ref{features-table} gives a compact listing
of all major capabilities present in the SymPy codebase. This grants a
sampling from the breadth of topics and application domains that SymPy
services. Unless stated otherwise, all features noted in
Table~\ref{features-table} are symbolic in nature. Numeric features are
discussed in Section~\ref{sec:numerics}.

>>>>

% Features to discuss in depth:
This section gives a basic introduction of SymPy, and lists its features.
A few features---assumptions, simplification, calculus, polynomials, printers,
solvers, and matrices---are core components of SymPy and are discussed in
depth. Many other features are discussed in depth in the supplementary
material.

\subsection{Basic Usage}
\label{sec:basic-usage}
\input{basic_usage.tex}

@@

Although SymPy's extensive feature set cannot be covered in depth in this
paper, calculus and other bedrock areas are discussed in their own
subsections. Additionally, Table~\ref{features-table} gives a compact listing
of all major capabilities present in the SymPy codebase. This grants a
sampling from the breadth of topics and application domains that SymPy
services. Unless stated otherwise, all features noted in
Table~\ref{features-table} are symbolic in nature. Numeric features are
discussed in Section~\ref{sec:numerics}.
